Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-29 demystify.tex
updates

Here are some general advice to find professor.  First, search for profs. that share similar research interests. You can learn about faculty and their level of research activity through the faculty's website or even from CSRankings.  For example, in CSRankings, if you want to work with PL, you can search for those publish in PL conferences.  If you want to work with SE \emph{and} AI, you can search for faculty who work in both SE and AI.   You can also go to their website, look at their papers and projects.  In any case, you should contact the professor and talk to them. For example, you can (cold) email them and ask about their research and if they are taking new students (\S\ref{sec:contact}) and schedule appointments to chat with them (office hrs are often the best time).

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Tenured, Tenure Track, Teaching,  Assistant Profs., Associate Profs, and Other Academic Titles}\label{sec:faculty-types}

Not every faculty in the CS program can serve as your formal adviser. Let's try to understand the different types of faculty and their roles. For example, you might hear about tenured,  tenure track, teaching faculty.  You might also things such as assistant, associate, full, adjunct, emeritus, teaching, research professors. Here is a primer on these terminologies.

@@

In contrast, \emph{teaching} (or instructional faculty or professor of practice) mainly focus on teaching. They typically teach 3-4 classes per semester and \emph{do not} have research responsibilities (e.g., they do not have to worry much about publishing papers, obtaining grants).  They can mentor Ph.D. students but they typically cannot serve as a formal adviser of Ph.D. students (i.e., they \emph{cannot graduate} PhD students).

>>>>

Here are some general advice to find professor.  First, search for profs. that share similar research interests. You can learn about faculty and their level of research activity through the faculty's website or even from CSRankings.  For example, in CSRankings, if you want to work with PL, you can search for those publish in PL conferences.  If you want to work with SE \emph{and} AI, you can search for faculty who work in both SE and AI.   You can also go to their website, look at their papers and projects.  In any case, you should contact the professor and talk to them. For example, you can (cold) email them and ask about their research and if they are taking new students (\S\ref{sec:contact}), and schedule appointments to chat with them (office hrs are often the best time).

@@

\subsubsection*{References}
\begin{itemize}
    \item \href{https://www.cs.columbia.edu/wp-content/uploads/2019/03/Get-Advisor.pdf}{The Definitive "what do I ask/look for" in a PhD Advisor Guide}
\end{itemize}
\subsection{Types of Faculty: Who can serve as a PhD adviser?}\label{sec:faculty-types}

Not every faculty can serve as your formal adviser. Let's try to understand the different types of faculty and their roles. For example, you might hear about tenured,  tenure track, teaching faculty.  You might also things such as assistant, associate, full, adjunct, emeritus, teaching, research professors. Here is a primer on these terminologies.

@@

In contrast, \emph{teaching} (or instructional faculty or professor of practice) mainly focus on teaching. They typically teach 3--4 classes per semester (which is quite a lot) and \emph{do not} have research responsibilities (e.g., they do not have to worry much about publishing papers, obtaining grants).  They can mentor Ph.D. students but they typically cannot serve as a formal adviser of Ph.D. students (i.e., they \emph{cannot graduate} PhD students).
